

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Sumit}{Agrawal}{ \urlstyle{same}\url{http://codewithgeeks.in} \\
\href{mailto:sumit4iit@gmail.com}{sumit4iit@gmail.com} | +91-9901444339
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\vspace{2.0mm}
\subsection{IIT, Indore}
\descript{B.Tech in Computer Science}
\location{APR 2014 | Indore \\ GPA: 9.0}
\sectionsep

\vspace{1.0mm}

\subsection{Balbhim College}
\descript{Class 12$^{th}$}
\location{MAY 2010 | Beed}
Maharshtra, Board of Higher Secondary \\
Education.
\location{ 85.0\% } 
\sectionsep

\vspace{1.0mm}

\subsection{NESJ, Jamner}
\descript{Class 10$^{th}$}
\location{MAY 2008 | Jamner}
New English School, Jamner \\
Maharshtra, Board of Secondary \\
Education.
\location{ 90.46.0\% } 
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/sumit4iit}{\custombold{Sumit Agrawal}} \\
LinkedIn://  \href{https://www.linkedin.com/in/sumit-agarwal-858a3844/}{\custombold{Sumit Agrawal}} \\
Quora://  \href{https://www.quora.com/profile/Sumit-Agrawal-6}{\custombold{Sumit Agrawal}}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
\textbullet{C++}
\textbullet{Java}
\textbullet{Python} \\ 
\location{Over 1000 lines:}
\textbullet{C}
\textbullet{bash}
\textbullet{HTML|CSS} \\
\location{Familiar:}
\textbullet{Android} \textbullet{PHP}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   
%     MISC
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{MISC}
\vspace{2.0mm}
\subsection{Responsibilities}
\textbullet{Served as an administrator of \href{http://fluxus.in}{\custombold{Fluxus}} and \href{http://placement.iiti.ac.in}{\custombold{IITI Placement Portal} at IIT Indore.}} \\
\textbullet{Wrote \href{http://academic.iiti.ac.in}{\custombold{academic portal}} of IIT Indore.}
\vspace{2.0mm}
\subsection{Competitions}
\textbullet{Won CISCO CTF as part of the SecConX 2015 at CISCO} \\
\textbullet{On Task 10 | Eudyptula Challenge}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\vspace{2.0mm}

\runsubsection{Arcesium India}
\descript{| Senior Member Technical}
\location{Oct 2015 – Present | Hyderabad, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space

\begin{tightemize}
\vspace{1.0mm}
\item Currently working on a DataRouter application. DataRouter abstracts out the complexities involved in extracting data from the counter-parties via different protocols. In the present form, DataRouter is limited to emails, it is being expanded to support other protocols such as SFTP and BBGMQ.

\vspace{1.0mm}

\item I worked on FRAMES framework, internal to Arcesium. FRAMES provides an easier way for applications to expose services via HTTP based APIs. FRAMES does the heavy lifting of generation of client side stubs. At present we support generation of Java, C\# and Python clients for the services exposed via FRAMES.

\vspace{1.0mm}

\item I was part of the Market Data Feeds team in Arcesium. I worked on fetching the market information such as prices, corporate actions from the third party vendors.
\end{tightemize}
\sectionsep

\runsubsection{CISCO Systems}
\descript{| Software Engineer }
\location{Aug 2014 – Sept 2015 | Bangalore India}
\begin{tightemize}
\vspace{1.0mm}
\item Worked on Exporter component of the Network Visibility Module, part of the Anyconnect Secure Mobility Client. Exporter module was responsible for transmitting collected endpoint information over the network in IPFIX format. I implemented IPFIX protocol.

\vspace{1.0mm}
\item Enabled automatic proxy detection while establishing vpn connection from Mac/ Linux based endpoints to the secure servers. This involved implementing Web Proxy Auto Discovery protocol, which allows automatic discovery of proxy servers.
\end{tightemize}
\sectionsep

\runsubsection{Microsoft IDC}
\descript{| Intern SDE}
\location{Summer 2013 | Bangalore India}
\begin{tightemize}
\item Implemented Acceptance Test Framework for UI automation. The framework was built on Selenium web driver.
\vspace{1.0mm}
\item I integrated the framework with the Microsoft Test Manager, for better reporting.

\end{tightemize}
\sectionsep

\section{Academic Projects}
\vspace{2.0mm}
\runsubsection{B. Tech Project} 
\descript{| Expression Invariant Face Recognition}
\location{IIT Indore | July 2013 - Mar 2014}
\begin{itemize}
\item Implemented a solution based on the Local Binary Patterns. The features extracted via LBP were used to train the classifier based on SVM. We relied upon the Cohn-Kanade's facial expression dataset to train the classifier.
\end{itemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\vspace{2.0mm}
\begin{tabular}{rll}
2010	     & IIT-JEE  & General Rank 3246 | Top 0.65\%\\
2010	     & AIEEE  & General Rank 4818 | Top 0.45\%\\
2008         & NTSE & Third Level \\
2006         & Silver Medalist & Dr. Homi Bhabha Jr. Scientist Competition
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}